Self Regulation Ontology Retest Analyses

### 2018-08-06 code/SRO_Retest_Analyses.Rmd
working on adding trial number info to figure

```{r}
trial_num_info = tmp %>%
  group_by(task_group) %>%
  summarise(mean_num_all_trials = round(mean(num_all_trials)),
            num_measures = length(unique(dv)))

@@

>>>>

```{r}
trial_num_info = tmp %>%
  group_by(task_group, task) %>%
  summarise(mean_num_all_trials = round(mean(num_all_trials)),
            num_measures = length(unique(dv)))

@@

Trying tableGrob

```{r warning=FALSE, message=FALSE}
mytheme <- gridExtra::ttheme_minimal(
    core = list(fg_params=list(cex = 3.5)),
    colhead = list(fg_params=list(cex = 3.0)),
    rowhead = list(fg_params=list(cex = 3.0)))

task_trial_num_table = tableGrob(trial_num_info %>% 
                                   filter(task == "task") %>% 
                                   ungroup() %>% 
                                   select(-task_group, -task),
                                 theme = mytheme, rows=NULL, cols = NULL,
                                 heights = rep(unit(1.25, "in"), 37))

test_plot = arrangeGrob(p4_t, task_trial_num_table, nrow=1)

ggsave('Task_Boot_w_trialinfo.jpg', plot = test_plot, device = "jpeg", path = "../output/figures/", width = 27, height = 48, units = "in", limitsize = FALSE, dpi = 100)
```

Trying geom_text

```{r warning=FALSE, message=FALSE}
task_trial_num = trial_num_info %>% 
  filter(task == "task") %>% 
  ungroup() %>% 
  select(-task)

task_trial_num_table = task_trial_num %>%
  mutate(y_axis = rev(seq(from=1, to=37, by=1))) %>%
  gather(key, value, -y_axis, -task_group) %>%
  ggplot(aes(key, y_axis))+
  geom_text(aes(label=value), size=14)+
  xlab("")+
  ylab("")+
  theme(axis.ticks=element_blank(),
        axis.text = element_blank(),
        panel.grid = element_blank(),
        panel.border = element_blank())
  # scale_x_discrete(position = "top",
  #                  breaks=c("mean_num_all_trials", "num_measures"),
  #                  labels=c("Mean Num Trials", "Num Measures"))

test_plot = arrangeGrob(p4_t, task_trial_num_table, nrow=1, widths = c(2,1))

ggsave('Task_Boot_w_trialinfo.jpg', plot = test_plot, device = "jpeg", path = "../output/figures/", width = 20, height = 48, units = "in", limitsize = FALSE, dpi = 100)
